Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-01-12 paper-1/manuscript.tex
Removed unclear/unnecessary/unfounded conclusion
Editing

In order to disentangle the effects of STD and TA, we ran all simulations in four conditions: Without any short-term plasticity, with either TA only or STD only, and with both STD and TA (labeled STD+TA in the following, and corresponding to the full model as described above). To turn off STD, we replaced Equation \ref{eqn-xsyn} with a constant $x = 1$, but retained the scaling of inputs to $g_e$ with $U$ in Equation \ref{eqn-gsyn}. This corresponds to immediate recovery ($\tau_x = 0$) and was done to maintain the magnitude of the excitatory postsynaptic potential (EPSP) in the recovered state regardless of whether STD was turned on or off. To turn off TA, we replaced Equation \ref{eqn-TA} with a constant $\theta = 0$, making the firing threshold completely unadaptive.

@@

To show that increased local suppression by STD reduces the non-target response, we correlated the median contrast in $D^B$ among the early portion of networks with the median contrast of the total response to B, echoing Figure \ref{fig6}e. As we show in Figure \ref{fig8}e, higher $\Delta D^B$ was clearly predictive of a lower network response ($\rho$ = -0.581, p = 1.81e-12; Wald test, n = 1000). This confirms again the integrity of the measure $D$, but also that STD-mediated local suppression played a role in reducing the non-target response in the \dev{} sequence.

>>>>

In order to disentangle the effects of STD and TA, we ran all simulations in four conditions: Without any short-term plasticity, with either TA only or STD only, and with both STD and TA (labeled STD+TA in the following, and corresponding to the full model as described above). To turn off STD, we replaced Equation \ref{eqn-xsyn} with a constant $x = 1$, but retained the scaling of inputs to $g_e$ with $U$ in Equation \ref{eqn-gsyn}. This corresponds to immediate recovery ($\tau_x = 0$) and was done to maintain the magnitude of the excitatory postsynaptic potential (EPSP) in the recovered state regardless of whether STD was turned on or off. To turn off TA, we replaced Equation \ref{eqn-TA} with a constant $V_{\theta} = \theta_0$, making the firing threshold completely unadaptive.

@@

To show that increased local suppression by STD reduces the non-target response, we correlated the median contrast in $D^B$ among the early portion of networks with the median contrast of the total response to B, echoing Figure \ref{fig6}e. As we show in Figure \ref{fig8}e, higher $\Delta D^B$ was clearly predictive of a lower network response ($\rho$ = -0.581, p = 1.81e-12; Wald test, n = 1000). This confirms that STD-mediated local suppression played a role in reducing the non-target response in the \dev{} sequence.
